%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% In The Name of God
%
%
% Parham Alvani Resume/CV
% parham.alvani@gmail.com
% https://github.com/1995parham
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv-fa} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\usepackage{parham-cv}

\begin{document}

% Your name and current job title/field
\header{پرهام}{الوانی}{دانشجوی مهندسی نرم افزار}


%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{\textcolor{TextYellow}{ا}رتباط}
دانشگاه امیرکبیر
خیابان حافظ
تهران، ایران
-
\lr{+98 (939) 090 9540}
\lr{+98 (21) 8802 13311}
-
\lr{\href{mailto:parham.alvani@gmail.com}{parham.alvani@gmail.com}}
\lr{\href{mailto:parham.alvani@aut.ac.ir}{parham.alvani@aut.ac.ir}}
\lr{\href{http://1995parham.github.io}{http://1995parham.github.io}}
\section{\textcolor{TextOrange}{ز}بان‌ها}
فارسی:
زبان مادری
انگلیسی:
تسلط محدود برای کار
\section{\textcolor{TextGreen}{ب}رنامه‌نویسی}
\lr{{\color{red} $\varheartsuit$} C, Go}
\lr{Python3, PHP}
\lr{AMD64 Assembly,}
\lr{AVR Assembly,}
\lr{Java SE, Java EE}
\lr{CSS3 \& HTML5}
\lr{NodeJs, JS}
\section{\textcolor{DarkBlue}{پ}روژه‌ها}
\lr{\href{https://github.com/1995parham}{\textcolor{TextGreen}{Github}}}
\section{\textcolor{Ocean}{آخرین}به روز رسانی}
\today
\end{aside}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{علایق}
\textbf{حرفه‌ای:}
\begin{itemize}
	\item اینترنت اشیا
	\item شبکه‌های نرم افزار بنیان
	\item مجازی سازی توابع شبکه
	\item \lr{Kernel Hacking}
	\item تئوری گراف
	\item آنالیز ریاضی
\end{itemize}
\textbf{شخصی:}
\begin{itemize}	
	\item شطرنج
	\item دویدن
\end{itemize}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{تحصیلات}

\begin{entrylist}

%------------------------------------------------

\entry
{۱۳۹۲-۱۳۹۶}
{کارشناسی, {\normalfont مهندسی کامپیوتر}}
{دانشگاه صنعتی امیرکبیر}
{معدل کل: ۱۹.۱۸ از ۲۰ (۸۷ واحد)}

%------------------------------------------------

\entry
{۱۳۸۸-۱۳۹۲}
{دبیرستان, {\normalfont دیپلم ریاضی و فیزیک}}
{دبیرستان انرژی اتمی}
{معدل کل: ۱۹.۴۵ از ۲۰}

%------------------------------------------------


\end{entrylist}

%----------------------------------------------------------------------------------------
%	HONORS and AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{جوایز و افتخارات}

\begin{entrylist}

%------------------------------------------------

\entry
{1394}
{{\normalfont فرصت انتخاب} \textcolor{TextGreen}{رشته دوم} {\normalfont به خاطر آمادگی}}
{}
{}

%------------------------------------------------

\entry
{بهار ۱۳۹۴}
{\normalfont Awarded as an Outstanding Student by the head of Computer Engineering and Information Technology department, AmirKabir University of Technology}
{}
{}

%------------------------------------------------

\entry
{بهار ۱۳۹۴}
{{\normalfont Achieved} \textcolor{TextYellow}{3rd} {\normalfont Place in 1st National Digital Design Contest of Iran CoDesign League as a Member of \emph{Polytechnic} team}}
{}
{}

%------------------------------------------------

\entry
{پاییز ۱۳۹۳}
{{\normalfont Achieved} \textcolor{UniBlue}{3rd} {\normalfont Place in 14th Amirkabir ACM International Collegiate Programming Contest (ICPC) as a Member of \emph{703} team}}
{}
{}

%------------------------------------------------

\entry
{پاییز ۱۳۹۳}
{\normalfont Participated in 39th Asia Regional ACM International Collegiate Programming Contest (ICPC) in Sharif University of Technology as a Member of \emph{703} team}
{}
{}

%------------------------------------------------

\entry
{۱۳۹۲}
{\normalfont Ranked in $0.2\%$ among more than $251,956$ participators in Nation-wide University Entrance Exam among all Iranian Students of Math. \& Physics}
{}
{}

%------------------------------------------------

\entry
{۱۳۹۰}
{\textcolor{TextOrange}{Semi-finalist} {\normalfont at National Mathematics and Computer Olympiads}}
{}
{}

%------------------------------------------------

\entry
{۱۳۸۹}
{\textcolor{TextOrange}{Semi-finalist} {\normalfont at National Mathematics and Computer Olympiads}}
{}
{}

%------------------------------------------------

\entry
{۱۳۸۸}
{\textcolor{TextOrange}{Semi-finalist} {\normalfont at National Mathematics and Computer Olympiads}}
{}
{}

%------------------------------------------------

\entry
{۱۳۸۸}
{{\normalfont Achieved} \textcolor{Ocean}{Merit Award} {\normalfont in the International Mathematics Competition (IMC) Icheon, South Korea}}
{}
{}

%------------------------------------------------

\entry
{۱۳۸۵-۱۳۸۸}
{\normalfont Member of National Organization for Development of Exceptional Talents \href{https://en.wikipedia.org/wiki/National_Organization_for_Development_of_Exceptional_Talents}{(NODET)}}
{}
{}


\end{entrylist}

%----------------------------------------------------------------------------------------
%       RESEARCH EXPERIENCE
%----------------------------------------------------------------------------------------

\section{تجربیات تحقیقاتی}

\begin{entrylist}

\entry
{2015-present}
{Department-wide platform for IoT and building management systems}
{under supervision of Prof.Bakhshi, Department of Computer Engineering and Information Technology, Amirkabir University of Technology, Tehran, Iran.}
{Research on different operating systems, frameworks and protocol stacks in IoT}

\end{entrylist}

%----------------------------------------------------------------------------------------
%       SKILLS and EXPERTISE
%----------------------------------------------------------------------------------------

\section{مهارت‌ها}

\begin{entrylist}

\entry
{\textcolor{TextGreen}{$\bullet$}}
{Functional Programming Languages}
{}
{SML, Lisp, Haskell}

%------------------------------------------------

\entry
{\textcolor{TextOrange}{$\bullet$}}
{Hardware Definition Languages}
{}
{Verilog HDL, VHDL, Spice}

%------------------------------------------------

\entry
{\textcolor{DarkBlue}{$\bullet$}}
{Networking Tools and Protocols}
{}
{ONOS Platform, FloodLight, Ryu, Mininet, GNS3, Wireshark, Cisco Packet Tracer, OpenFlow1.3}

%------------------------------------------------

\entry
{\textcolor{Ocean}{$\bullet$}}
{Typesetting}
{}
{\LaTeX, Microsoft Word, LibreOffice, Pages, Vim}

%------------------------------------------------

\entry
{\textcolor{LightGray}{$\bullet$}}
{Hardware Simulators}
{}
{Xilinx Vivado Design Suite, P-Spice, H-Spice, Proteus, Quartus II}

%------------------------------------------------

\entry
{\textcolor{TextYellow}{$\bullet$}}
{DB Management Systems}
{}
{MySQL, PostgreSQL, MongoDB}

%------------------------------------------------

\entry
{\textcolor{TextRed}{$\bullet$}}
{Operating Systems}
{}
{Ubuntu, Ubuntu Server, CentOS, OS X, Windows, Windows Server 2012}

%------------------------------------------------

\entry
{\textcolor{TextPink}{$\bullet$}}
{Other}
{}
{Netbeans, IntelliJ, Eclipse, Octave, Matlab}

%------------------------------------------------

\entry
{\textcolor{UniBlue}{$\bullet$}}
{Programming Framework}
{}
{
	\textbf{C Frameworks}
	\begin{itemize}
		\item CGI Programming
		\item BSD Socket Programming
		\item UNIX System Programming
		\item GTK
		\item Gnome
	\end{itemize}
	
	\textbf{Java Frameworks}
	\begin{itemize}
		\item Maven
		\item Log4j
		\item JPA(Java Persistence API)
		\item Hibernate
		\item JSP
		\item JSF
	\end{itemize}
}

%------------------------------------------------


\end{entrylist}

%----------------------------------------------------------------------------------------
%       TEACHING EXPERIENCES
%----------------------------------------------------------------------------------------

\section{تجربیات تدریس}

\begin{entrylist}

\entry
{Fall 2014}
{Principles of Computer and Programming}
{Teaching Assistant}
{Amirkabir University of technology, Under Supervision of Prof. Bakhshi.}

%------------------------------------------------

\entry
{Spring 2015}
{Advance Programming}
{Teaching Assistant}
{Amirkabir University of technology, Under Supervision of Prof. Noorhosseini.}

%------------------------------------------------

\entry
{Spring 2015}
{Discrete Mathematics}
{Teaching Assistant}
{Amirkabir University of technology, Under Supervision of Prof. Fallah.}

%------------------------------------------------

\entry
{Spring 2015}
{Introduction to Python Programming}
{Instructor}
{7th Amirkabir Linux Festival, Python Workshop}

%------------------------------------------------

\entry
{Fall 2015}
{Principles of Computer and Programming}
{Teaching Assistant}
{Amirkabir University of technology, Under Supervision of Prof. Bakhshi.}

%------------------------------------------------

\entry
{Spring 2016}
{Advance Programming}
{Teaching Assistant}
{Amirkabir University of technology, Under Supervision of Prof. Noorhosseini.}

%------------------------------------------------

\entry
{Spring 2016}
{Principles of Database Design}
{Teaching Assistant}
{Amirkabir University of technology, Under Supervision of Prof. Momtazi.}

%------------------------------------------------

\entry
{Spring 2016}
{Microprocessor I}
{Teaching Assistant}
{Amirkabir University of technology, Under Supervision of Prof. Homayounpour.}

%------------------------------------------------

\entry
{Spring 2016}
{Engineering Statistics and Probability}
{Teaching Assistant}
{Amirkabir University of technology, Under Supervision of Prof. Amir Haeri.}

%------------------------------------------------


\end{entrylist}

%----------------------------------------------------------------------------------------
%       GRADUATE COURSES
%----------------------------------------------------------------------------------------

\section{درس‌های ارشد}

\begin{entrylist}

\entry
{پاییز ۱۳۹۴}
{شبکه‌های کامپیوتری پیشرفته}
{پروفسور خرسندی}
{}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%       CERTIFICATIONS
%----------------------------------------------------------------------------------------

\section{مدارک}
\begin{itemize}
	\item \lr{CompTIA Network+}
	\item \lr{Supporting Windows 8.1(70-688)}
	\item \lr{Installing and Configuring Windows Server 2012(70-410)}
	\item \lr{Administering Windows Server 2012(70-411)}
	\item \lr{Configuring Advanced Windows Server 2012 Services(70-412)}
	\item \lr{Designing and Implementing a Server Infrastructure(70-413)}
	\item \lr{Implementing an Advanced Server Infrastructure(70-414)}
	\item \lr{LPIC-1(101-102)}
	\item \lr{LPIC-2(201-202)}
	\item \lr{Cisco CCENT}
\end{itemize}

\end{document}

